### 2020-04-22 dataclean.tex
tweaks

As most analysis software uses table-like data, we fill the needed
repeats of values missing in the raw data (see
Fig.~\ref{fig:dataraw}). First, we reduce the data to the GPU that
were removed later than 2013 to focus our analysis epoch on units
installed in the second rework cycle or later. After this reduction,
there were stil six older units remaining, which we also removed to
have a clean third epoch set of units for the analysis. We do some
further processing to handle time overlaps in a tiny fraction (under
0.0007 in GPU life and 0.0002 in location life) of recorded life in
the raw records by simply dropping the overlapping life times.

>>>>

As most analysis software relies on rectangular table-like data, we
fill the needed repeats of values missing in the raw data (see
Fig.~\ref{fig:dataraw}). To focus our analysis on data after the first
two rework cycles in the break-in period, we first reduce the data to
the GPUs that were installed shortly before 2014 started. This was
done by removing data for any units with a {\em remove} date before
2014. After this reduction, there were stil six older units remaining,
which we also removed to have a clean set of units for the
analysis. We do some further processing to handle time overlaps in a
tiny fraction (under 0.0007 in GPU life and 0.0002 in location life)
of recorded life in the raw records by simply dropping the overlapping
life times.
